\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation

### 2018-05-04 ccs/ex.tex
ccc

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in \sectionref{impl}).

@@

>>>>

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in \sectionref{impl}).
\dg{We discuss the choices made by our compiler below in \sectionref{ccc}.}

@@

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
\dg{Points to address. 1. hard problem nto solve optimally 2. some decisions are fixed and some are context sensitive 3. our heuristics and their basis}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. We analyse these costs by running microbenchmarks for basic operations and interconversions and obtained numers consistent with ABY~\cite{aby} (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean. However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use some heuristics based on costs observed using microbenchmarking. Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.
